{\Large \bf Analysing time course microarray data using Bioconductor: a case study using yeast2 Affymetrix arrays}

### 2012-07-11 paper.Rnw
Added sessionInfo() to the paper.

\section{List of R packages}

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
Package & Version & Package & Version \\
\midrule
affy & \Sexpr{packageDescription("affy")$Version}   & IRanges & \Sexpr{packageDescription("IRanges")$Version} \\
affyPLM & \Sexpr{packageDescription("affyPLM")$Version}  & limma & \Sexpr{packageDescription("limma")$Version} \\
AnnotationDbi & \Sexpr{packageDescription("AnnotationDbi")$Version} & Mfuzz & \Sexpr{packageDescription("Mfuzz")$Version} \\
ArrayExpress & \Sexpr{packageDescription("ArrayExpress")$Version} & timecourse & \Sexpr{packageDescription("timecourse")$Version}  \\
Biobase & \Sexpr{packageDescription("Biobase")$Version}  & yeast2probe & \Sexpr{packageDescription("yeast2probe")$Version} \\
Biostrings & \Sexpr{packageDescription("Biostrings")$Version} & yeast2cdf & \Sexpr{packageDescription("yeast2cdf")$Version} \\
gcrma & \Sexpr{packageDescription("gcrma")$Version}  & \\
\bottomrule
\end{tabular}
\caption{List of packages from Bioconductor used in this paper.}\label{AT.1}
\end{table}

<<echo=FALSE>>=
#library()
@

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
Package & Version & Package & Version \\
\midrule
bitops & \Sexpr{packageDescription("bitops")$Version}  & GeneNet & \Sexpr{packageDescription("GeneNet")$Version} \\
caTools & \Sexpr{packageDescription("caTools")$Version} & gplots & \Sexpr{packageDescription("gplots")$Version} \\ 
corpcor & \Sexpr{packageDescription("corpcor")$Version} & grid & \Sexpr{packageDescription("grid")$Version} \\
e1071 & \Sexpr{packageDescription("e1071")$Version}  & gtools & \Sexpr{packageDescription("gtools")$Version}  \\
fdrtool & \Sexpr{packageDescription("fdrtool")$Version} & MASS & \Sexpr{packageDescription("MASS")$Version} \\
gdata & \Sexpr{packageDescription("gdata")$Version}  & longitudinal &
\Sexpr{packageDescription("longitudinal")$Version}  \\
\bottomrule

\end{tabular}
\caption{List of packages from the CRAN repository used in this paper.}\label{AT.2}

\end{table}

<<eval=TRUE>>=
version
@

>>>>

\section{Session Information}

% \begin{table}[h]
% \centering
% \begin{tabular}{@{}llll@{}}
% \toprule
% Package & Version & Package & Version \\
% \midrule
% affy & \Sexpr{packageDescription("affy")$Version}   & IRanges & \Sexpr{packageDescription("IRanges")$Version} \\
% affyPLM & \Sexpr{packageDescription("affyPLM")$Version}  & limma & \Sexpr{packageDescription("limma")$Version} \\
% AnnotationDbi & \Sexpr{packageDescription("AnnotationDbi")$Version} & Mfuzz & \Sexpr{packageDescription("Mfuzz")$Version} \\
% ArrayExpress & \Sexpr{packageDescription("ArrayExpress")$Version} & timecourse & \Sexpr{packageDescription("timecourse")$Version}  \\
% Biobase & \Sexpr{packageDescription("Biobase")$Version}  & yeast2probe & \Sexpr{packageDescription("yeast2probe")$Version} \\
% Biostrings & \Sexpr{packageDescription("Biostrings")$Version} & yeast2cdf & \Sexpr{packageDescription("yeast2cdf")$Version} \\
% gcrma & \Sexpr{packageDescription("gcrma")$Version}  & \\
% \bottomrule
% \end{tabular}
% \caption{List of packages from Bioconductor used in this paper.}\label{AT.1}
% \end{table}
% 
% <<echo=FALSE>>=
% #library()
% @
% 
% \begin{table}[h]
% \centering
% \begin{tabular}{@{}llll@{}}
% \toprule
% Package & Version & Package & Version \\
% \midrule
% bitops & \Sexpr{packageDescription("bitops")$Version}  & GeneNet & \Sexpr{packageDescription("GeneNet")$Version} \\
% caTools & \Sexpr{packageDescription("caTools")$Version} & gplots & \Sexpr{packageDescription("gplots")$Version} \\ 
% corpcor & \Sexpr{packageDescription("corpcor")$Version} & grid & \Sexpr{packageDescription("grid")$Version} \\
% e1071 & \Sexpr{packageDescription("e1071")$Version}  & gtools & \Sexpr{packageDescription("gtools")$Version}  \\
% fdrtool & \Sexpr{packageDescription("fdrtool")$Version} & MASS & \Sexpr{packageDescription("MASS")$Version} \\
% gdata & \Sexpr{packageDescription("gdata")$Version}  & longitudinal &
% \Sexpr{packageDescription("longitudinal")$Version}  \\
% \bottomrule
% 
% \end{tabular}
% \caption{List of packages from the CRAN repository used in this paper.}\label{AT.2}
% 
% \end{table}

<<eval=TRUE>>=
sessionInfo()
@
